---
title: "OKC Internship Assessment"
author: "Memphis Lau"
date: '2022-10-10'
output: pdf_document
---

Here I will read in the data:
```{r}
shots <- read.csv("shots_data.csv")
```


## Adding New Column Data
This function tells me whether a shot is a 2-pointer or 3-pointer based on the x and y positions, which I can use to create a new column in my table that shows whether each shot is a 2-pointer or not.
```{r}
two_pointer <- function(x, y){
  output <- logical(length(x))
  for(i in 1:length(x)){
    if (y[i] <= 7.8){
      if (x[i] <= 22){
        output[i] <- TRUE
      }
    } else {
      if ((x[i]^2 + y[i]^2) <= (23.5)^2){
        output[i] <- TRUE
      }
    }
  }
  output
}
```

```{r}
shots$two_point_shot <- as.numeric(two_pointer(shots$x, shots$y))
head(shots, n = 5)
```


Now I add a column that says whether the shot was a corner three pointer or not.
```{r}
shots$corner_three <- as.numeric((shots$two_point_shot == 0) & (shots$y <= 7.8))
head(shots, n = 5)
```

## Separating by Team
```{r}
team_a <- shots[shots$team == "Team A", ]
team_b <- shots[shots$team == "Team B", ]
```

## Shot distribution

### Team A
```{r}
total_shots <- nrow(team_a)

# Two point shots
sum(team_a$two_point_shot) / total_shots

# Non-Corner Three
(total_shots - sum(team_a$two_point_shot) - sum(team_a$corner_three)) / total_shots

# Corner Three
sum(team_a$corner_three) / total_shots
```

So 72.5% of Team A's shots were two-pointers, 24.3% were non-corner three pointers, and 3.2% were corner threes.

### Team B
```{r}
total_shots <- nrow(team_b)

# Two point shots
sum(team_b$two_point_shot) / total_shots

# Non-Corner Three
(total_shots - sum(team_b$two_point_shot) - sum(team_b$corner_three)) / total_shots

# Corner Three
sum(team_b$corner_three) / total_shots
```
69.2% of Team B's shots were two-pointers, 27.7% were non corner three pointers, and 3.1% were corner threes.

## Effective Field Goal Per Zone
### Team A
```{r}
# 2 pointers
team_a_2PT <- team_a[team_a$two_point_shot == 1, ]
sum(team_a_2PT$fgmade) / nrow(team_a_2PT)

# Non Corner Three
team_a_NC3 <- team_a[team_a$two_point_shot == 0 & team_a$corner_three == 0, ]
1.5 * sum(team_a_NC3$fgmade) / nrow(team_a_NC3)

# Corner Three
team_a_C3 <- team_a[team_a$corner_three == 1, ]
1.5 * sum(team_a_C3$fgmade) / nrow(team_a_C3)
```
For Team A, the efg for 2PT, NC3, and C3 are 50.2%, 46.3%, and 33.3%, respectively.


### Team B
```{r}
# 2 pointers
team_b_2PT <- team_b[team_b$two_point_shot == 1, ]
sum(team_b_2PT$fgmade) / nrow(team_b_2PT)

# Non Corner Three
team_b_NC3 <- team_b[team_b$two_point_shot == 0 & team_b$corner_three == 0, ]
1.5 * sum(team_b_NC3$fgmade) / nrow(team_b_NC3)

# Corner Three
team_b_C3 <- team_b[team_b$corner_three == 1, ]
1.5 * sum(team_b_C3$fgmade) / nrow(team_b_C3)
```
For Team B, the efg for 2PT, NC3, and C3 are 43.9%, 50.8%, and 64.3%, respectively.

Though the samples are very small, it seems the data tells us that Team B should attempt more corner threes. The data also aligns well in that Team B makes threes at a higher percentage than Team A, and thus shoots more threes proportionally.